Paper figures

### 2020-12-21 notebooks/paper_plots_0909.Rmd
notebooks with all analyses i have until Dec 21st 2020

with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)
with open(f'data/interim/yuri_0916/yuri.pickle','rb') as f:
    e_yuri = pickle.load(f)
with open(f'data/interim/huri_0916/huri.pickle','rb') as f:
    e_huri = pickle.load(f)
with open(f'data/interim/gi_1201/gi_100.pickle','rb') as f:
    e_gi = pickle.load(f)

@@

pcc_degree_dens <- 
    plot_density_prs(pcc_df, deg, xlab='Degree')
pcc_eff_dens <- 
    plot_density_prs(pcc_df, eff_norm, xlab='Effectiveness')
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
pcc_sensitivity_dens <- 
    plot_density_prs(pcc_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network", fontface='bold')
pcc_dens_comb = cowplot::plot_grid(pcc_degree_dens+theme(legend.position='none'), 
                                pcc_eff_dens+theme(legend.position='none'), 
                                pcc_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
gi_degree_dens <- 
    plot_density_prs(gi_df, deg, xlab='Degree')
gi_eff_dens <- 
    plot_density_prs(gi_df, eff_norm, xlab='Effectiveness')
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
gi_sensitivity_dens <- 
    plot_density_prs(gi_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network GI", fontface='bold')
gi_dens_comb = cowplot::plot_grid(gi_degree_dens+theme(legend.position='none'), 
                                gi_eff_dens+theme(legend.position='none'), 
                                gi_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
gi_dens_comb_title = cowplot::plot_grid(title, gi_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
yuri_degree_dens <- 
    plot_density_prs(yuri_df, deg, xlab='Degree')
yuri_eff_dens <- 
    plot_density_prs(yuri_df, eff_norm, xlab='Effectiveness')
yuri_sensitivity_dens <- 
    plot_density_prs(yuri_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("Yeast PPI network", fontface='bold')
yuri_dens_comb = cowplot::plot_grid(yuri_degree_dens+theme(legend.position='none'), 
                                yuri_eff_dens+theme(legend.position='none'), 
                                yuri_sensitivity_dens+theme(legend.position='none'), labels=c('D','E','F'),ncol=3)
yuri_dens_comb_title = cowplot::plot_grid(title, yuri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
huri_degree_dens <- 
    plot_density_prs(huri_df, deg, xlab='Degree')
huri_eff_dens <- 
    plot_density_prs(huri_df, eff_norm, xlab='Effectiveness')
huri_sensitivity_dens <- 
    plot_density_prs(huri_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("HuRI network", fontface='bold')
huri_dens_comb = cowplot::plot_grid(huri_degree_dens+theme(legend.position='none'), 
                                huri_eff_dens+theme(legend.position='none'), 
                                huri_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
huri_dens_comb_title = cowplot::plot_grid(title, huri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
dens_plots = cowplot::plot_grid(pcc_dens_comb_title,
                                gi_dens_comb_title,
                                yuri_dens_comb_title,
                                huri_dens_comb_title,nrow=4)
cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
ggsave('reports/figures/paper_figures_1204_withgi/fig1.png')

@@

#    coord_trans(x = "log10", y = "log1p")
#    scale_x_continuous(trans = "log10")
    #scale_x_log10()
#    geom_histogram(binwidth=1)+
#    xlim(1,NA)+
#    ylim(NA, 0.1)
ggsave('tmp.png')

@@

                   huri_deg_eff, huri_deg_sens, labels = c('A','','B','','C',''),

@@

```{r}
pcc_rewire_df = read_csv('data/interim/pcc_0909/rewire_data.csv')
gi_rewire_df = read_csv('data/interim/gi_1201/rewire_data.csv')
yuri_rewire_df = read_csv('data/interim/yuri/rewire_data.csv')
huri_rewire_df = read_csv('data/interim/huri/rewire_data.csv')

@@

```{r}
network_labels  <- c('Costanzo 2016','Costanzo GI','Yeast PPI','HuRI')
#p3 = ggplot(rewire_df, aes(x=eff_deg_pearson))+
#    stat_density(geom = "line", trim=TRUE)+
##    geom_histogram(binwidth = 0.001)+
#    geom_vline(xintercept=0.9,color='red')+
#    theme_bw()

@@

p3 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Effectiveness degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"))+
    scale_y_continuous(expand = c(0, 0)) 
p4 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Sensitivity degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
    scale_color_discrete(labels=c('Rewired networks', 'Real network'))+
    scale_y_continuous(expand = c(0, 0)) 
lgn34  <- cowplot::get_legend(p4)
distr_plots <- plot_grid(
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=3, labels=c('D','E','','F','G',''), rel_heights = c(0.45,0.45,0.1))
#ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)

plot_grid(deg_scatter_plots, distr_plots, nrow=2,rel_heights = c(0.6,0.4))
ggsave('reports/figures/paper_figures_1204_withgi/fig3.png',width=8,height=9)
```

@@

```{r}
sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_0915/sensor_connectivity_df.csv')%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))

@@

#p3 = 
sensor_connectivity_plot <- 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =sensor_connectivity_df%>%filter(type!='real'),aes(x=ratio,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =sensor_connectivity_df%>%filter(type=='real'),aes(xintercept=ratio,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Ratio of between group edges to outgroup edges')+
    theme_bw()+
    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
    theme(legend.position='bottom')+
    scale_y_continuous(expand = c(0, 0))

#p3 = 
    ggplot()+
    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
                 aes(x=data,y=ratio,color=type))+
#    geom_jitter()+
    geom_vline(data=sensor_connectivity_df%>%filter(type=='real'),
            aes(x=data,y=ratio,color=type, group=data))+
               #position=position_jitter(), aes(shape=data))+
    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
    scale_x_discrete(labels=network_labels)+
  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
    theme_bw()

neighbor_degree_plot <- combined_df%>%filter(group=='real')%>%group_by(data)%>%
    mutate(is_sensor = factor(ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE), levels=c(TRUE,FALSE)))%>%
#    mutate(is_sensor = fct_relevel(is_sensor,c(TRUE,FALSE)))%>%
    ggplot(aes(x=is_sensor,y=log(neighbor_degree)))+
    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
#    geom_point()+
    geom_boxplot()+
    theme_bw()+
    ylab('Log(Average neighbor degree)')+
    xlab('')+ stat_compare_means()+
    scale_x_discrete(labels=c('aensor', 'Not Sensor'))
plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
ggsave('reports/figures/paper_figures_0916/fig5.png')

>>>>

with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)
with open(f'data/interim/yuri_1205/yuri.pickle','rb') as f:
    e_yuri = pickle.load(f)
with open(f'data/interim/huri_1205/huri.pickle','rb') as f:
    e_huri = pickle.load(f)
with open(f'data/interim/gi_1205_0.2/gi_100.pickle','rb') as f:
    e_gi = pickle.load(f)

@@

pcc_degree_dens <- 
    plot_density_prs(pcc_df, deg, xlab='Degree')
pcc_eff_dens <- 
    plot_density_prs(pcc_df, eff_norm, xlab='Effectiveness')
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
pcc_sensitivity_dens <- 
    plot_density_prs(pcc_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
pcc_dens_comb = cowplot::plot_grid(pcc_degree_dens+theme(legend.position='none'), 
                                pcc_eff_dens+theme(legend.position='none'), 
                                pcc_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
gi_degree_dens <- 
    plot_density_prs(gi_df, deg, xlab='Degree')
gi_eff_dens <- 
    plot_density_prs(gi_df, eff_norm, xlab='Effectiveness')
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
gi_sensitivity_dens <- 
    plot_density_prs(gi_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("Yeast Genetic Interaction", fontface='bold')
gi_dens_comb = cowplot::plot_grid(gi_degree_dens+theme(legend.position='none'), 
                                gi_eff_dens+theme(legend.position='none'), 
                                gi_sensitivity_dens+theme(legend.position='none'), labels=c('D','E','F'),ncol=3)
gi_dens_comb_title = cowplot::plot_grid(title, gi_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
yuri_degree_dens <- 
    plot_density_prs(yuri_df, deg, xlab='Degree')
yuri_eff_dens <- 
    plot_density_prs(yuri_df, eff_norm, xlab='Effectiveness')
yuri_sensitivity_dens <- 
    plot_density_prs(yuri_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("Yeast PPI network", fontface='bold')
yuri_dens_comb = cowplot::plot_grid(yuri_degree_dens+theme(legend.position='none'), 
                                yuri_eff_dens+theme(legend.position='none'), 
                                yuri_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
yuri_dens_comb_title = cowplot::plot_grid(title, yuri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
huri_degree_dens <- 
    plot_density_prs(huri_df, deg, xlab='Degree')
huri_eff_dens <- 
    plot_density_prs(huri_df, eff_norm, xlab='Effectiveness')
huri_sensitivity_dens <- 
    plot_density_prs(huri_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("HuRI network", fontface='bold')
huri_dens_comb = cowplot::plot_grid(huri_degree_dens+theme(legend.position='none'), 
                                huri_eff_dens+theme(legend.position='none'), 
                                huri_sensitivity_dens+theme(legend.position='none'), labels=c('J','K','L'),ncol=3)
huri_dens_comb_title = cowplot::plot_grid(title, huri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
dens_plots = cowplot::plot_grid(pcc_dens_comb_title,
                                gi_dens_comb_title,
                                yuri_dens_comb_title,
                                huri_dens_comb_title,nrow=4)
cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
ggsave('reports/figures/paper_figures_1204_withgi/fig1.png', width=8,height=12)

@@

#    coord_trans(x = "log10", y = "log1p")
#    scale_x_continuous(trans = "log10")
    #scale_x_log10()
#    geom_histogram(binwidth=1)+
#    xlim(1,NA)+
#    ylim(NA, 0.1)
#ggsave('tmp.png')

@@

                   huri_deg_eff, huri_deg_sens, labels = c('A','','B','','C','','D',''),

@@

```{r}
pcc_rewire_df = read_csv('data/interim/pcc_0909/rewire_data.csv')
gi_rewire_df = read_csv('data/interim/gi_1205_0.2/rewire_data.csv')
yuri_rewire_df = read_csv('data/interim/yuri_1205/rewire_data.csv')
huri_rewire_df = read_csv('data/interim/huri_1205/rewire_data.csv')

@@

```{r}
network_labels  <- c('Yeast GI Profile Similarity','Yeast Genetic Interaction','Yeast PPI','HuRI')
#p3 = ggplot(rewire_df, aes(x=eff_deg_pearson))+
#    stat_density(geom = "line", trim=TRUE)+
##    geom_histogram(binwidth = 0.001)+
#    geom_vline(xintercept=0.9,color='red')+
#    theme_bw()

@@

p3 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Effectiveness degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"))+
    scale_y_continuous(expand = c(0, 0)) 
p4 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Sensitivity degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
    scale_color_discrete(labels=c('Rewired networks', 'Real network'))+
    scale_y_continuous(expand = c(0, 0)) 
lgn34  <- cowplot::get_legend(p4)
distr_plots <- plot_grid(
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=3, labels=c('E','F',''), rel_heights = c(0.45,0.45,0.1))
#ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
plot_grid(deg_scatter_plots, distr_plots, nrow=2,rel_heights = c(0.6,0.4))
ggsave('reports/figures/paper_figures_1204_withgi/fig3.png',width=10,height=12)
```

@@

@@

sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/sensor_connectivity_df.csv')%>%
    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))
#p3 = 
sensor_connectivity_plot <- 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =sensor_connectivity_df%>%filter(type!='real'),aes(x=ratio,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =sensor_connectivity_df%>%filter(type=='real'),aes(xintercept=ratio,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Ratio of between group edges to outgroup edges')+
    theme_bw()+
    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
    theme(legend.position='bottom')+
    scale_y_continuous(expand = c(0, 0)) 
##p3 = 
#    ggplot()+
#    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
#                 aes(x=data,y=ratio,color=type))+
##    geom_jitter()+
#    geom_vline(data=sensor_connectivity_df%>%filter(type=='real'),
#            aes(x=data,y=ratio,color=type, group=data))+
#               #position=position_jitter(), aes(shape=data))+
#    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
#    scale_x_discrete(labels=network_labels)+
#  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
#    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
#    theme_bw()
neighbor_degree_plot <- combined_df%>%filter(group=='real')%>%group_by(data)%>%
    mutate(is_sensor = factor(ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE), levels=c(TRUE,FALSE)))%>%
#    mutate(is_sensor = fct_relevel(is_sensor,c(TRUE,FALSE)))%>%
    ggplot(aes(x=is_sensor,y=log(neighbor_degree)))+
    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
#    geom_point()+
    geom_boxplot()+
    theme_bw()+
    ylab('Log(Average neighbor degree)')+
    xlab('')+ stat_compare_means()+
    scale_x_discrete(labels=c('aensor', 'Not Sensor'))
plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
ggsave('reports/figures/paper_figures_1204_withgi/fig5.png')
